Motion Planning for Assessing the Accessibility of Protein Tunnels

### 2018-02-26 paper.tex
image updated
final version for ral

\documentclass[usletter, 10pt, conference]{ieeeconf} % initial submission to RAL/ICRA
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{subfig}
\usepackage[ruled,lined]{algorithm2e}
\usepackage{multirow}
\usepackage{color}
\usepackage{flushend}
\usepackage[bookmarks=false]{hyperref}
\usepackage{setspace} % for setstretch in algorithm
\pdfminorversion=4

@@

\title{Assessing the Accessibility of Protein Tunnels using Motion Planning}

@@

\begin{table}[t]
\caption{\label{tab::m040c}
\small
Examples of elongated/packed conformation for m040 (1,5-Dichloropentane).
The table shows the average number of different ligand conformations (out of 50) used in trajectories reaching the active site in the 4E46 protein.
}
\centering
{\footnotesize
%\def\arraystretch{0.9}
\begin{tabular}{cc}
\rotatebox{0}{\hskip 5pt Long} \\ \includegraphics[width=0.07\textwidth]{fig/m040-conf1} \\
\rotatebox{0}{Packed} \\ \includegraphics[width=0.0375\textwidth]{fig/m040-conf2}
\end{tabular}
}
{\scriptsize
\def\arraystretch{0.9}
\input usedc.tex
}
\end{table}

@@

%The case was the analysis of Leukotriene A4 hydrolase (PDB ID 4L2L).
The task of the second analysis was to find the trajectory for the ligand 4-(4-benzylphenyl)-1,3-thiazol-2-amine into the active
site of A4 hydrolase (PDB ID 4L2L, 9666 atoms).
%This ligand is a known inhibitor of the protein 4L2L.
%Based on the location of inhibitor inside the protein we assume that the inhibitor is able 
The tCONCOORD tool~\cite{seeliger2007geometry} was used to generate 1000 conformations of the protein 4L2L.
The initial PDB structure was minimized by GROMACS 4.0.7
%\cite{hess2008gromacs} 
 using the input parameters recommended on the example page of tCONCOORD~\cite{tconcoord}.
The protein conformations were generated using the default settings for tCONCOORD in the PERT mode. % which only perturbs the starting configuration of atoms instead of complete randomization.
The tunnels leading to the active site defined by residues 134 (Alanine) and 311 (Phenylalanine) were computed by CAVER 3.0, using the probe 0.9~\AA.
All 1000 conformations contained at least 5 tunnels, more than 900 conformations contained 9 tunnels.
The ordering of the detected tunnels slightly differs in different conformations.
Therefore, the ligand traversability towards the active site was computed for the first three widest tunnels (with average bottlenecks 1.22~\AA, 1.20~\AA\, and 1.19~\AA\ with the average lengths 22.3~\AA, 25.3~\AA\, and 28.4~\AA, respectively).
The conformations of the ligand were prepared in the same way as in the previous section.
From the available $|\L|=736$ low-energy conformations, 100 were selected using the `S' strategy.

@@

\begin{figure}
\centering
\vskip -5pt
\includegraphics[width=0.4\textwidth]{fig/4l2l-solution}
\caption{\small
    \label{fig::inhibitor}Example of a trajectory inside the tunnel No. 1 of the 4L2L protein with the final position of the ligand.
}
\end{figure}

>>>>

\documentclass[usletter, 10pt, conference]{ieeeconf} % initial submission to RAL/ICRA
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{subfig}
\usepackage[ruled,lined]{algorithm2e}
\usepackage{multirow}
\usepackage{color}
\usepackage{flushend}
\usepackage[bookmarks=false]{hyperref}
\usepackage{setspace} % for setstretch in algorithm
%\usepackage[all]{nowidow}
\pdfminorversion=4

@@

\title{
%Assessing the Accessibility of Protein Tunnels using Motion Planning % ICRA title
Motion Planning for Assessing the Accessibility of Protein Tunnels  %iros title, we had to change it
}

@@

\begin{table}[t]
\caption{\label{tab::m040c}
\small
Examples of elongated/packed conformation for m040 (1,5-Dichloropentane).
The table shows the average number of different ligand conformations (out of 50) used in trajectories reaching the active site in the 4E46 protein.
}
\centering
{\footnotesize
%\def\arraystretch{0.9}
\begin{tabular}{cc}
\rotatebox{0}{\hskip 5pt Long} \\ \includegraphics[width=0.07\textwidth]{fig/m040-conf1} \\
\rotatebox{0}{Packed} \\ \includegraphics[width=0.055\textwidth]{fig/m040-conf2}
\end{tabular}
}
{\scriptsize
\def\arraystretch{0.9}
\input usedc.tex
}
\end{table}

@@

%The case was the analysis of Leukotriene A4 hydrolase (PDB ID 4L2L).
The task of the second analysis was to find the trajectory for the ligand 4-(4-benzylphenyl)-1,3-thiazol-2-amine into the active
site of A4 hydrolase (PDB ID 4L2L, 9666 atoms).
%This ligand is a known inhibitor of the protein 4L2L.
%Based on the location of inhibitor inside the protein we assume that the inhibitor is able 
The tCONCOORD tool~\cite{seeliger2007geometry} was used to generate 1000 conformations of the protein 4L2L.
The initial PDB structure was minimized by GROMACS 4.0.7
%\cite{hess2008gromacs} 
 using the input parameters recommended on the example page of tCONCOORD~\cite{tconcoord}.
The protein conformations were generated using the default settings for tCONCOORD in the PERT mode. % which only perturbs the starting configuration of atoms instead of complete randomization.
The tunnels leading to the active site defined by residues 134 (Alanine) and 311 (Phenylalanine) were computed by CAVER 3.0, using the probe 0.9~\AA.
All 1000 conformations contained at least 5 tunnels. % more than 900 conformations contained 9 tunnels.
The ordering of the detected tunnels slightly differs in different conformations.
Therefore, the first three widest tunnels were used (with average bottlenecks 1.22~\AA, 1.20~\AA\, and 1.19~\AA\ with the average lengths 22.3~\AA, 25.3~\AA\, and 28.4~\AA, respectively).
20 starting configurations were found at the begining of each tunnel, and 10 trajectories were computed for each starting configuration.
The conformations of the ligand were prepared in the same way as in the previous section.
From the available $|\L|=736$ low-energy conformations, 100 were selected using the `S' strategy.

@@

\begin{figure}
\centering
\vskip -5pt
\includegraphics[width=0.4\textwidth]{fig/4l2l-solution}
\caption{\small
    \label{fig::inhibitor}Example of a found trajectory inside the tunnel No. 1 of the 4L2L protein with the final position of the ligand.
}
\end{figure}
